Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area.

### 2022-07-07 outputs/paper/paper.qmd
Updates to paper

pollution %>% filter(pollutant != "CO") %>% ggplot(
  aes(x = month_name, y = mean_pollution, color = pollutant)) + geom_point() + 
  labs(color="Pollutant") + xlab("Month") + ylab("Mean Pollution (ppb)")

>>>>

level_order <- c("Jan", "Feb","Mar", "Apr", "May", "Jun", "Jul", "Aug","Sep", "Oct","Nov", "Dec")

pollution %>% filter(pollutant != "CO") %>% ggplot(
  aes(x = factor(month_name, level = level_order), y = mean_pollution, color = pollutant)) + geom_point() + 
  labs(color="Pollutant") + xlab("Month") + ylab("Mean Pollution (ppb)")
